HPC Final Project

### 2019-05-16 report/draft.tex
Fix some typo
Fix some typo in the report

For NuFFT of type 1, introducing a free parameter $\eta$, we have that
\begin{equation}
\sum_{n=1}^{N} \mathbf{f}_n e ^{i \mathbf{k} \cdot \mathbf{x}_m }  = e^{\eta k^2 / 8 \xi^2} \sum_{n=1}^{N} \mathbf{f}_n e^{-\eta k^2 / 8 \xi^2} e ^{-i (\mathbf{-k}) \cdot \mathbf{x}_m }  := e^{\eta k^2 / 8 \xi^2} \hat{H}_{\mathbf{-k}}
\end{equation}
while $\hat{H}_{\mathbf{k}}$ is the inverse Fourier transform of 
\begin{equation}
H(\mathbf{x}) = \left(\frac{2 \xi^2}{\pi \eta}\right)^{3/2}  \sum_{n=1}^N \mathbf{f}_n e^{-2 \xi^2 |\mathbf{x} - \mathbf{x}_n|_{\ast}^2 / \eta} \label{eq:gaussian_gridding_1}
\end{equation}
where $|\cdot|_{\ast}$ denotes distance to closest periodic image. (\textit{Remark from Guanchun: The distance is a little weird, I haven't checked if it's the inverse Fourier transform or not. Is it common in periodic setting?})

>>>>

For NuFFT of type 1, introducing a free parameter $\eta$, we have that
\begin{equation}
\sum_{n=1}^{N} \mathbf{f}_n e ^{i \mathbf{k} \cdot \mathbf{x}_m }  = e^{\eta k^2 / 8 \xi^2} \sum_{n=1}^{N} \mathbf{f}_n e^{-\eta k^2 / 8 \xi^2} e ^{-i (\mathbf{-k}) \cdot \mathbf{x}_m }  := e^{\eta k^2 / 8 \xi^2} \hat{H}_{\mathbf{-k}}
\end{equation}
while $\hat{H}_{\mathbf{k}}$ is the Fourier transform of 
\begin{equation}
H(\mathbf{x}) = \left(\frac{2 \xi^2}{\pi \eta}\right)^{3/2}  \sum_{n=1}^N \mathbf{f}_n e^{-2 \xi^2 |\mathbf{x} - \mathbf{x}_n|_{\ast}^2 / \eta} \label{eq:gaussian_gridding_1}
\end{equation}
where $|\cdot|_{\ast}$ denotes distance to closest periodic image. (\textit{Remark from Guanchun: The distance is a little weird, I haven't checked if it's the Fourier transform or not. Is it common in periodic setting?})
